Long groovy title goes here

### 2013-06-27 shanghai.tex
Poor Tate, the quote from his thesis is now gone.

%\input{introduction}
In his celebrated thesis, John Tate writes 
\begin{quotation}
    {\it Concerning the characters of $k^*$ [the
    multiplicative group of a $\mathfrak{p}$-adic field], the
    situation is different from that of $k^+$.  First of all, we are
    interested in continuous multiplicative maps $\alpha \mapsto
    c(\alpha)$ of $k^*$ into the complex numbers, not only in the
    bounded ones, and shall call such a map a quasi-character,
    reserving the word ``character'' for the conventional character of
    absolute value $1$. Secondly, we shall find no model for the group
    of quasi-characters, or even for the group of characters, though
    such a model would be of the utmost importance.}
  \cite{Tate:thesis}*{\S 2.3}
\end{quotation}
\noindent
In this paper we show that the monidal category of character sheaves
on the Greenberg transform of the locally finite type Neron model of
$T$ provides an elegant, canonical model for the group of
(quasi-)characters of $T(K)$, where $K$ is any non-Archimedean local
field and $T$ is any algebraic torus over $K$.

>>>>

%\input{introduction}
%In his celebrated thesis, John Tate writes 
%\begin{quotation}
%    {\it Concerning the characters of $k^*$ [the
%    multiplicative group of a $\mathfrak{p}$-adic field], the
%    situation is different from that of $k^+$.  First of all, we are
%    interested in continuous multiplicative maps $\alpha \mapsto
%    c(\alpha)$ of $k^*$ into the complex numbers, not only in the
%    bounded ones, and shall call such a map a quasi-character,
%    reserving the word ``character'' for the conventional character of
%    absolute value $1$. Secondly, we shall find no model for the group
%    of quasi-characters, or even for the group of characters, though
%    such a model would be of the utmost importance.}
%  \cite{Tate:thesis}*{\S 2.3}
%\end{quotation}
%\noindent
In this paper we show that the monidal category of character sheaves
on the Greenberg transform of the locally finite type Neron model of
$T$ provides an elegant, canonical model for the group of
(quasi-)characters of $T(K)$, where $K$ is any non-Archimedean local
field and $T$ is any algebraic torus over $K$.
